Handling missing data in smartphone location logs

### 2018-05-03 Thesis Report/thesisReport.Rmd
restructure and organise

Having thus converted lattitude and longitude onto coordinates unique to each individual, let a person's true location on this two-dimensional plane be $G(t) = [G_x(t) G_y(t)]$ where $G_x(t)$ and $G_y(t)$ denote the location of the individual at time $t$ on the x-axis and y-axis respectively. Moreover, let $D \in \mathbb{R}^2$ be the recorded data containing lattitude and longitude. In addition, let $a$ denote the estimated accuracy of the recorded data.  accuracy. $G(t)$, $D$ and $a$ are indexed by time labled by the set $T = t_1 < ... < t_{n+1}$. For simplicity, let each entry in the discrete index set $T$ represent a 5 minute window. The measure of accuracy $a_t$ is given in meters such that it represents the radius of a 67% confidence circle. If $D_t = \emptyset$ it is considered *missing* and it is not missing otherwise.

>>>>

Having thus converted lattitude and longitude onto coordinates unique to each individual, let a person's true location on this two-dimensional plane be $G(t) = [G_x(t) G_y(t)]$ where $G_x(t)$ and $G_y(t)$ denote the location of the individual at time $t$ on the x-axis and y-axis respectively. Moreover, let $D \in \mathbb{R}^2$ be the recorded data containing lattitude and longitude. In addition, let $a$ denote the estimated accuracy of the recorded data.  accuracy. $G(t)$, $D$ and $a$ are indexed by time labled by the countable set $t = t_1 < ... < t_{n+1}$. For simplicity, let each entry in the discrete index set $t$ represent a 5 minute window. The measure of accuracy $a_t$ is given in meters such that it represents the radius of a 67% confidence circle. If $D_t = \emptyset$ it is considered *missing* and it is not missing otherwise.

When several data sets are available from individuals living in overlapping areas we can construct a $t \times i$ matrix $M$ where the entry $M(t,i)$ contains $G(t)$ for the individual $i$.
